Methodology for Assessing the State of the Practice for Domain X

### 2020-09-28 StateOfPractice/Methodology/Methodology.tex
updated section 9 of Methodology

\section{Measure Using Measurement Template} \label{SecShallowMeasure}
For each software package fill out one column of the \href{run:Combined_MeasurementTemplate_EmpiricalMeasures.xlsx}{Measurement Template} spreadsheet found in our repository. Follow these steps:
\ad{Maybe a one or two sentences introduction to the template?} \pmi{SS:"A screenshot of a portion of the template would be very helpful here"}

\pmi{SS:"please add an estimate of how long each measurement typically takes"}

\pmi{SS:"explain any tricky parts with interpreting the parameters of variation for measuring a particular indicator. A few example would help."}

\begin{enumerate} 
	\item Gather the summary information into the top section of the document
	\item Using the GitStats tool found in Section \ref{gitstats} gather the measurements for the Repo Metrics - GitStats section found near the bottom of the document
	\item Using the SCC tool found in Section \ref{scc} gather the measurements for the Repo Metrics - SCC section found near the bottom of the document
	\item If the software package is found on git, gather the measurements for the Repo Metrics - GitHub section found near the bottom of the document
	\item Review installation documentation and attempt to install the software package on a virtual machine
	\item Gather the measurements for installability
	\pmi{SS:"we should mention that the project owners will be contacted for help with installation, if necessary, but that there is a cap on the amount of time spent on installation"}
	\item Gather the measurements for correctness and verifiability
	\item Gather the measurements for surface reliability
	\item Gather the measurements for surface robustness
	\item Gather the measurements for surface usability
	\item Gather the measurements for maintainability
	\item Gather the measurements for reusability
	\item Gather the measurements for surface understandability
	\item Gather the measurements for visibility and transparency
	\item Assign a score out of ten for each quality \pmi{SS:"add some text about how the measure out of 10 is assigned for each quality", link to scoring document}
\end{enumerate}
\pmi{SS:"add something about the sensitivity analysis tool and its purpose", explain what the tool is and its purpose, indicate that it will be used in the next section to verify rankings, add it to the next section}

>>>>

\section{Measure Using Measurement Template} \label{SecShallowMeasure}

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=1.0\textwidth]{measurement_template}
		\caption{Top of Measurement Template}
		\label{measurement_template_image}

	\end{center}
\end{figure}

The \href{run:Combined_MeasurementTemplate_EmpiricalMeasures.xlsx}{Measurement Template} is used to track measurements and quality scores for all of the software packages in the domain. For each software package, fill out one column of the template. This process can take between 2 to 5 hours for each package.
Project developers can be contacted for help regarding installation, if necessary, but a cap of about 2 hours should be imposed on the entire installation process. For completing the template, please follow these steps:

\pmi{SS:"explain any tricky parts with interpreting the parameters of variation for measuring a particular indicator. A few example would help."}\pmi{Ask Ao for input}

\begin{enumerate} 
	\item Gather the summary information into the top section of the document (Figure \ref{measurement_template_image})
	\item Using the GitStats tool that is described in Section \ref{SecEmpiricalMeasures} gather the measurements for the Repo Metrics - GitStats section found near the bottom of the document
	\item Using the SCC tool that is also described in Section \ref{SecEmpiricalMeasures} gather the measurements for the Repo Metrics - SCC section found near the bottom of the document
	\item If the software package is found on git, gather the measurements for the Repo Metrics - GitHub section found near the bottom of the document
	\item Review installation documentation and attempt to install the software package on a virtual machine
	\item Gather the measurements for installability
	\item Gather the measurements for correctness and verifiability
	\item Gather the measurements for surface reliability
	\item Gather the measurements for surface robustness
	\item Gather the measurements for surface usability
	\item Gather the measurements for maintainability
	\item Gather the measurements for reusability
	\item Gather the measurements for surface understandability
	\item Gather the measurements for visibility and transparency
	\item Assign a score out of ten for each quality. The score can be measured using the \href{run:MeasurementTemplate_ImpressionCalculator.xlsx}{Measurement Template Impression Calculator}. For each quality measurement, the file indicates the appropriate score to assign the measurement based on possible measurement values.
\end{enumerate}
